Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-06-28 ProbabilisticCoherence.tex
Changes to Section 4.3 - still incomplete

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
\subsection{Elliptical Distributions}
We now show that if the mapping $g(.)$ in definition $\ref{def:reconpoint}$ is extended to allow for a translation by ${\bm d}$, i.e. $g({\bm y})={\bm G}{\bm y}+{\bm d}$, then the true predictive distribution can be recovered for elliptical distributions.  Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions. 
\begin{theo}[Reconciliation for Elliptical Distributions]
	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.  Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.  Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density, where $\bm\Omega$ is the true variance covariance matrix of the predictive distribution for the bottom level. 
\end{theo}
\begin{proof}
   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).  The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.  The reconciled scale matrix is 
   \begin{align*}
   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}{\bm \Sigma}{\bm\Sigma}^{-1/2}{\bm\Omega}^{1/2}{\bm S}'\\
   =&{\bm S}{\bm \Omega}{\bm S}'\\
   =&{\bm \Sigma}
   \end{align*}
   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location matrix is 
   \begin{align*}
   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)\\
   =&{\bm S}{\bm G}_{opt}\hat{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}{\bm \mu}\\
   =&{\bm S}{\bm G}_{opt}{\bm \mu}\\
   =&{\bm \mu}\\
   \end{align*}
   The final equality above holds since ${\bm S}{\bm G}_{opt}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace and ${\bm S}{\bm G}_{opt}{\bm \mu}={\bm \mu}$.
\end{proof}	
It should be noted that ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.  However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.  To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$. For arbitrary ${\bm G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.  This approximation has similarities with the way bottom level estimates are produced for point forecast reconciliation.  Rather than mapping a vector of point forecasts to reconcilied bottom level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.  The value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$. While it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.

>>>>

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
%\end{equation}
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
\subsection{Elliptical Distributions}
We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.  Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions. 
\begin{theo}[Reconciliation for Elliptical Distributions]
	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.  Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.  Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is the true variance covariance matrix of the predictive distribution for the bottom level. 
\end{theo}
\begin{proof}
   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).  The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.  The reconciled scale matrix is 
   \begin{align*}
   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm A}{\bm\Sigma}^{-1/2}{\bm \Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm A}'{\bm S}'\\
   =&{\bm S}{\bm \Omega}{\bm S}'\\
   =&{\bm \Sigma}
   \end{align*}
   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location vector is 
   \begin{align*}
   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}\\
   =&{\bm \mu}\\
   \end{align*}
\end{proof}	
A number of insights can be drawn from this theorem.  First, although a linear mapping $g(.)$ can be used to recover the true density in the elliptical case, the same does not hold in general.  Second, $g(.)$ is not, in general, a projection matrix.  Third, ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.

\todo{Some discussion about why projections are good}.

%However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.  To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$. For arbitrary ${\bm G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.  This approximation has similarities with the way bottom level estimates are produced for point forecast reconciliation.  Rather than mapping a vector of point forecasts to reconcilied bottom level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.  The value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$. While it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
